\section{Functional requirements}

\makeatletter
\def\requirement#1#2{\begingroup
   \def\@currentlabelname{#2}%
   \label{#1}\endgroup
  #2}
\makeatother

\def \reqref#1 {
  \ref{#1}. \nameref{#1}.
}

\subsection{Must have}
The prototype must have the following features:

\begin{enumerate}
\item \emph{\requirement{req:search}{Search for a video};}\\
The prototype must have a search bar in which the user types the name of the video the user is looking for, then the prototype should show a number of names of videos which closely, if not fully, resemble the searched name.

\item \emph{\requirement{req:play}{Play the selected video};}\\
When the user has selected a video from the before mentioned list, the user can then press a play button. After pressing the play button, the prototype will play the selected video.

\item \emph{\requirement{req:pause}{Pause the video};}\\
While playing the video, the user can press a pause button which will pause the video. The video can then be resumed by pressing the play button.

\item \emph{\requirement{req:seek}{Seek in the video};}\\
A slider will be at the bottom of the video, with which the user can set the slider to a certain part of the video. The prototype then resumes play at that part of the video.

\subsection{Should have}
\item \emph{\requirement{req:download}{Download the selected video};}\\
The user can choose to download a video by means of pressing a download button so the user can watch it later instead of watching it immediately.

\subsection{Could have}
\item \emph{\requirement{req:channel}{Browse through 'channels' for videos};}\\
The desktop version of tribler has channels that allows users to browse through a collection of videos, a similar feature could be implemented in the prototype.

\subsection{Would have}
\item \emph{\requirement{req:seed}{Seed a video};}\\
While watching and downloading the video is only leeching, also seeding the already downloaded pieces of the video would increase the availability of pieces in the swarm.

\item \emph{\requirement{req:upload}{Upload a video};}\\
The user can upload videos from his own gallery.

\item \emph{\requirement{req:platform}{Make the application available for other mobile platforms};}\\
The prototype will only be made on the mobile platform: Android. It would however, be good to branch out to other mobile platforms such as iOS and Windows mobile in order to attract more users.r

\end{enumerate}

