\section{Trade-off}
\label{sec:trade_off_mobplat}
The trade-off will be made according to several criteria. Table \ref{tab:trade_off_mob} is provided in which a number of criteria are set out. The market share of the different mobile platforms will be described in Section \ref{sec:mark_share}, followed by the proficiency of the team in relation to the different programming languages. Finally, a conclusion to which mobile platform is chosen for the prototype is provided.

\subsection{Market share}
\label{sec:mark_share}
In the second quarter of 2013, research was conducted by Strategy Analytics\footnote{\url{http://www.strategyanalytics.com/}} in to the global market share of the different mobile platforms. The result is that Android holds a 79.5\% market share, iOS has a 13.6\% share and Microsoft has a share of 3.9\%\footnote{http://news.cnet.com/8301-1035\_3-57596548-94/android-nabs-record-80-percent-market-share-in-q2/}.  Android has the biggest share and this means that an application in Android will most likely have a larger user base than its iOS or Windows Phone counterpart.

\subsection{Programming language}
The team is proficient with C, C++, C\#, Java and script languages such as Javascript, XML, PHP, etc. They also have some experience with making applications for Android. Further more they do not own a Mac computer or iPhone. 

\subsection{Conclusion}
Concluding, Android is chosen as mobile platform because it has the largest market share and the team is more capable of developing applications for Android than for any other mobile platform.

\begin{savenotes}
\begin{table}[h]
\begin{center}
\caption{A trade off between three mobile platforms 
\label{tab:trade_off_mob}}
	\begin{tabularx}{\textwidth}{|X|X|X|X|}
	\hline
	& Windows Phone & Apple iOS & Google Android\\ \hline
	
	Number of Applications Available 
	& 160.000\footnote{http://thenextweb.com/microsoft/2013/06/27/microsoft-windows-phones-160000-apps-see-more-than-200-million-downloads-monthly/\label{downloads}} 
	& 900.000\footnote{\url{http://www.apple.com/pr/library/2013/06/10Apple-Unveils-iOS-7.html}} 	
	& 800.000\footnote{\url{http://www.appbrain.com/stats/number-of-android-apps}} \\ \hline
	
	Number of Total Application Downloads 
	& ? (200 million per month\footnote{via footnote \ref{downloads}}) 
	& 50 billion total\footnote{\label{note1}http://ben-evans.com/benedictevans/2013/5/16/how-many-apps-do-android-and-ios-users-download}
	& 48 billion total\footnote{via footnote \ref{note1}} \\ \hline 

	Number of Different Tablets and Phones 
	& 27\footnote{\url{http://www.windowsphone.com/en-us/phones}}$^{,}$\footnote{http://reviews.cnet.com/8301-3121\_7-57531284-220/windows-8-the-complete-new-pc-launch-list/}
	& 19\footnote{8 iPhone models, 5, iPod Touch models, 4 iPad models, iPad Mini and Apple TV}
	& 3997+\footnote{http://techcrunch.com/2012/05/15/3997-models-android-fragmentation-as-seen-by-the-developers-of-opensignalmaps/} \\ \hline
	
	Application Development Languages 
	& C\#\footnote{\url{http://www.microsoft.com/en-us/download/details.aspx?id=7029}}, VB.NET\footnote{\url{http://msdn.microsoft.com/en-us/vstudio/hh388573}}, C++\footnote{\url{http://isocpp.org/}}, Javascript\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/JavaScript?redirectlocale=en-U0\&redirectslug=JavaScript}}, F\#\footnote{\url{http://fsharp.org/}} 
	& Objective-C\footnote{\url{http://developer.apple.com/library/mac/documentation/Cocoa/Conceptual/ProgrammingWithObjectiveC/Introduction/Introduction.html}}.
	& Java\footnote{\url{http://www.java.com/}}, XML\footnote{\url{http://www.w3.org/TR/REC-xml/}}, C/C++ \\ \hline
	
	Market Share\footnote{http://news.cnet.com/8301-1035\_3-57596548-94/android-nabs-record-80-percent-market-share-in-q2/}		& 3.9\% & 13.6\% & 79.5\% \\ \hline

	\end{tabularx}
\end{center}
\end{table}
\end{savenotes}