\section{Video on Demand services}
\label{sec:vodserv}
The following VoD services are chosen because of their popularity, others were left out because they were less known, provided less functionality, less range of content or their cost was higher than one of the following services:

\subsection{ITV Player}
ITV Player is a VoD service which shows the programs broadcast on the channels ITV1, ITV2, ITV3, ITV4 and CITV. It provides playback for shows up to 7 days after they aired on TV and after a free registration this becomes 30 days. The range of programs shown is therefor limited to those that were aired, these range from TV-shows and live shows such as X-factor. The ITV Player is available on the website\footnote{http://www.itv.com} on a desktop environment (Mac, Windows and Linux), PlayStation 3, iOS and Android\footnote{https://www.itv.com/itvplayer/help/faq/1}. The ITV player does show advertisement before playback of every chosen video.

\subsection{Amazon Instant Video}
Amazon has a VoD service in which the user pays a yearly fee and can buy and rent videos from their web store. A lot of content is free to watch after the yearly fee is paid, but other releases may not be and must be bought or rented digitally. The application with which to watch the videos is available for: Windows, Kindle Fire (HD), Apple devices, PlayStation 3, Xbox 360, Wii (U), a number of set-top boxes\footnote{http://www.amazon.com/gp/feature.html?ie=UTF8\&docId=1000663511} and the so called: `smart TVs'\footnote{http://www.businessinsider.com/what-is-a-smart-tv-2010-12}.

\subsection{Youtube}
Youtube started in 2005 and has quickly become the most popular VoD service. As said in section \ref{sec:motivation}, one billion unique users visit Youtube every month, adding up to 6 billion hours of videos watched each month. The service is available for desktop environments, Android, iOS, Windows Phone, game consoles and smart TVs. The videos available for playback are all added by users themselves. Anyone can upload a video, including companies that want to add a video of their latest product or news stations covering the latest events, but also videos of a kid's soccer match can be uploaded. There are limits to what is allowed which is included in their policy\footnote{https://www.youtube.com/yt/policyandsafety/policy.html}.

\subsection{Netflix}
Netflix is a streaming VoD service that allows users to watch an unlimited amount of videos after paying a low monthly fee (\$7.99 per month at the time of writing this). It includes movies and TV programs and is available only in the United States, Canada, Latin America, the United Kingdom and Ireland. As of July 2013 it has 37.6 million users in total\footnote{http://news.yahoo.com/numbers-netflix-subscribers-205626746.html}. Netflix is available on Windows, Mac, Android, iOS, Windows Phone, set-top boxes, smart TVs and game consoles\footnote{http://www.netflix.com/NetflixReadyDevices}.