\section{August 1st, 2013}

The meeting was opened at 10.00

\begin{enumerate}
\item Review agenda:\\		
Agenda is accepted

\item Review of prior minutes:\\		
No further remarks about the prior minutes are made.

\item Sprint planning\\
\begin{enumerate}
\item[-] Completed tasks during last sprint:\\
The team reports that more time is needed for the completion of the Orientation Report. The team states that it is still working on the video decoding sections, and that several other sections of the report still need to be extended and reviewed before release. The team says it can finish the remaining work by the end of the week. The supervisor adresses the fact that the team should be aware of time consumption during the current phase of the project; losing an additional week means losing 1/6th of the available implementation time. Implementation time, according to the Supervisor, is really critical for this project, and should be safeguarded as much as possible.\\

Additional adivce is given by the Supervisor in relation to the (software) components that will be used in the project. The Supervisor advises the team to individually check each component to see if it works under Android. He also notes that the team first should only focus on being able to stream something. Only after this core functionality has been achieved, the team should focus on further improvements or additional features.\\

The Supervisor re-addresses the fact that the team should do a sanity check on all components to really verify if these components will really run on an Android environment. The Supervisor also asks the team if there already is a component available to run Python code on Android. The team states that there is already a working component written by Ed Knutson, that does exactly that. The team also says that Libswift runs on Android.\\

\item[-] Encountered impediments:\\
Apart from the previously mentioned difficulties, no further impediments are reported by the Team.

\item[-] Tasks to do during upcoming sprint:\\
The team and Supervisor both note that the Orientation Report needs to be finished, and a deadline is set on Sunday, August 4th (end of day).  The Supervisor also notes that a task distribution, covering all of the project work, should be added to the Orientation Report as an appendix. The team notes that the design documents, consisting of the RAD document, Architectural Design Document, TDD, and Test- and Implementation Plan needs to be finished by the end of the next sprint. The Supervisor and the team both agree on the fact that the RAD document will take most of the time. The Supervisor also adds that the requirements should be validated in accordance with the Client. The Test- and Implementation Plan will only take around an hour, according to the Supervisor. The team and Supervisor both agree on setting the deadline for the design documents at Wednesday, August 7th. All design documents will be sent by e-mail to both the Supervisor and the Client. Finally, the Supervisor says he will try to set up the next progress meeting such that the Client can be present as well, as to facilitate the requirements validation.
\end{enumerate}
	
\item Other Issues:\\
No other issues were reported by the team nor the Supervisor.\\
\end{enumerate}
There were no further questions and the meeting was ended at 10.35
