\section{September 12th, 2013}

The meeting was opened at 10.03.\\

\begin{enumerate}
\item Review agenda\\	
The agenda is accepted.
\item Review of prior minutes\\
Prior minutes are accepted.
\item Sprint planning\\
\begin{enumerate}
\item[-] Completed tasks during last sprint.\\
	\begin{itemize}
	\item Boost\\
Boost is compiled for Android, this library is needed for libtorrent.
Thanks to Egbert, the Team can now compile libtorrent as well, through a russian tracker application for android.
	\end{itemize}
\item[-] Encountered impediments\\
	\begin{itemize}
	\item SIG\\
There is no code to hand in to SIG, so this wasn't done and the Supervisor ensured the Team that this was no issue.
	\item Boost \& libtorrent
The team said that they took a long time finding out how to build boost and libtorrent so a quite some time was lost here. The Supervisor and Client understood this and as example they said that a professor took a full-time week to build libtorrent for Mac.
	\end{itemize}
\item[-] Libtorrent\\
The Team will now implement libtorrent in their own project to make it simple, fast and responsive. They will use it to download a torrent file and then let it play through a seperately compiled VLC for now.
\item[-] Streaming\\
After making an app that downloads a torrent through the libtorrent wrapper, the Team will implement the streaming function. To get a video to stream, The Client said that Egbert wrote a wrapper class that does this on a desktop environment for python code. The Team will look at this wrapper to see how it is done and how they can achieve this for android.
\end{enumerate}
\item Other issues\\
No other issues were reported.
\end{enumerate}

There were no questions.\\

The meeting was closed at 10.25.\\
