\chapter{Work Division}
\label{sec:work_div}
This chapter clarifies who wrote the different chapters and it shows the division in the implementation phase. The division of the report is as follows:

\section{Report}
\begin{itemize}
\item Plan of Action\\
Martijn and Jaap wrote this together.
\item Orientation\\
	Martijn wrote the following sections:
	\begin{itemize}
	\item Video Decoding Frameworks
	\item Risk analysis
	\end{itemize}
	Jaap wrote the rest:
	\begin{itemize}
	\item Introduction
	\item Mobile Platforms
	\item Video on Demand on (non-)Mobile Devices
	\end{itemize}
\item Requirements\\
Initially Jaap set this up. Martijn processed the feedback from the meeting with the client (see Appendix \ref{sec:req_meet}).
\item Test and Implementation plan\\
Jaap wrote this.
\item Architectural Design\\
Jaap wrote the following section:
	\begin{itemize}
	\item System composition
	\end{itemize}
And Martijn wrote the rest:
	\begin{itemize}
	\item Persistent data management
	\item Concurrency
	\item Software control
	\item Boundary conditions
	\end{itemize}
\item Implementation Phase \\
Jaap wrote this.
\item Final Phase \\
Jaap wrote this.
\item Appendices \\
Martijn wrote the outline of the VLC compilation guide, Jaap finalized it. Jaap wrote the Libtorrent guide. Furthermore, Jaap wrote all the minutes, as well as the agendas for these meetings. 
\end{itemize}

\section{Implementation}
Jan-Willem did about 40\% of the work in the implementation phase, which contains most of the GUI and the combining of VLC and Libtorrent. Jaap did the other 60\%, which includes figuring out how to compile the different libraries, such as Libtorrent, Boost and VLC.
