\documentclass[pdftex, 12pt, a4paper]{report}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}

\begin{document}

\pagestyle{fancy}
\fancyhead[CE, CO] {Minutes Mobile VoD}
\fancyhead[LE, LO] {\today}

The meeting was opened at 15.39

\begin{enumerate}
\item Review agenda\\		
Agenda is accepted
	
\item Planning\\
The supervisor said that the gantt-chart of the planning is good, but watch out with extending your own deadlines. It shouldn't happen that if we extend it one week now that it turns to six weeks at the end. The TU Delft will base the grade mostly on the report, the client on the product.The supervisor also said that another group first did the problem description,then the orientation report and after that the Plan of Action. The team said they are busy with the plan of action and will write the orientation report after this, so the problem description in the Plan of Action is kept broad on purpose.

\begin{enumerate}
\item Plan of action\\
The supervisor asked the team to hand in the first draft on monday before 11.00 am. The team explained they are finalizing the last chapter. After a bit of talk about a risk analysis, the decided to put a reference in the plan of action, and a more detailed version in the orientation report.

\item Orientation report\\
The supervisor asked the team to hand in the first draft on monday before 11.00 am. And the weekend after the final version, after the supervisor has reviewed the document. Trade-off's are good to have in an orientation report, explained the supervisor, also explain only the chosen one in detail and give a brief overview of the rest of the possibilities. 

\item Planning of the rest of the project \\
The supervisor recommended that one week to make a final report is not a lot of time, so spend less time on design (excl. requirements) and change it later during implementation the team has more time for the implementation.

\end{enumerate}
\item Other issues\\
The supervisor recommended to keep the client up to date, especially about the requirements document.
In the near future a meeting with the supervisor, client and the team should be planned, said the supervisor. Another issue he adressed was that the team should make sure the testtablets come early; it shouldn't be so that the team has to wait two weeks when they want to start testing on a tablet.

\end{enumerate}

There were no further questions and the meeting was ended at 16.05
\end{document}
