\documentclass[pdftex, 12pt, a4paper]{report}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}

\begin{document}

\pagestyle{fancy}
\fancyhead[CE, CO] {Minutes Mobile VoD}
\fancyhead[LE, LO] {August 22nd, 2013}

The meeting was opened at 10.00

\begin{enumerate}
\item Review agenda	\\	
Agenda is accepted.
\item Review of prior minutes\\
The previous minutes were accepted.
\item Sprint planning
\begin{enumerate}
\item[-] Encountered impediments\\
The team said that the Orientation Report takes up more time than originally thought, but it is in the stage for the first review.
\item[-] Orientation Report\\
The supervisor said to take up the timing in the risk analysis, it entails when a decision to, for example, use a different solution must be made.\\
The supervisor stressed that at the next meeting the team should know if VLC will work or not.\\

All documents should be done by Sunday.
\item[-] Requirements Analysis Document\\
\item[-] Architectural Design Document\\
The team said that they have not yet started work on this document.
\item[-] Technical Design Document\\
The Supervisor and team agreed that this document should be pulled in with the architectural document.
\item[-] Test- and Implementation Plan\\
The plan to do test-driven development(TDD) should be revised, because it is not suitable for this project. Manual tests according to the requirements should be done, and unit tests must be included.
The plan of action should be revised to exclude TDD.\\
\end{enumerate}
\item Other issues\\
The supervisor stressed that more hours should be spent on the project, on average most people spend 45-50 hours per week.\\
Both the Supervisor and the team were curious how SIG would evaluate the code that we include from other sources such as Tribler and VLC. The team should contact SIG to see how this will be evaluated.

\end{enumerate}
There were no further questions.\\

\noindent The meeting was closed at 10.25.\\

\end{document}
